Automated Program Verification and Synthesis of Embedded \& Cyber-physical Systems: Advances and Challenges

### 2017-08-08 paper.tex
addition to section 4

Generally, state-of-the-art verification methodologies for embedded systems generate test vectors (with constraints) and use some assertion-based verification and high-level processor models, during simulation~\cite{Behrend15,Lettnin09}, as shown in Figure~\ref{verification-methodologies}. 
%
\begin{figure}[h]
	\centering
	\includegraphics[scale=0.5]{figure4.jpg}
	\caption{Verification methodologies for embedded systems.}
	\label{verification-methodologies}
\end{figure}

@@

Indeed, the first two aspects are of extreme relevance in micro-grids and cyber-physical systems, in order to ensure reliability, which is a key issue for (smart) cities, industries, and consumers, and the third one is essential in systems that implement device models, such as digital filters and controllers, which present a behavior that is highly dependent on signal inputs and outputs and whose deployment may be heavily affected by hardware restrictions. The fourth aspect deals with code that relies on existing infrastructures and must be compliant with those, such as Linux kernel modules. The fifth aspect, in turn, is inherent to a large number of embedded systems from  telecommunications, control systems, and medical devices. In particular, software developed for that type of embedded systems has been extensively tested and verified, and also optimized for efficiency over years of development. Therefore, when a new product is derived from a given platform, a lot of legacy code is usually reused for improving development time and code quality. The sixth aspect is related to evolving development processes and technologies, which may delay the application of suitable verification and synthesis approaches, if verifiers and synthesizers do not support different programming languages and interfaces. The seventh aspect highlights a subjective task in verification: where one must insert an evaluation point or assertion, in order to correct address a property. The eighth one is related to the widespread use of embedded systems in autonomous-vehicle navigation systems~\cite{Adouane16}, which demands optimization solving during their execution for a wide range of functions, including non-linear and non-convex problems using fixed- and floating-point arithmetic. The ninth aspect is a consequence of changes in environment or different applications and scenarios, which may present new problems to embedded systems that did not exist or were not tackled during their development. Such a challenge is also closely related to ML techniques, given that they may be integrated into commercial systems and have the potential to devise new and refined control strategies, which must then be identified, checked, and validated. For instance, a diagnostic system may employ techniques that make it able to learn new tumor patterns and them warn their presence on patients' bodies, but a wrong updated model may compromise earlier traditional assessments and erroneously perform new ones, which should be verified and validated. Finally, the latter also raises another question: an embedded system must be checked only when it is developed/created or also during its life cycle, in order to ensure that improved models and actions are sound and reliable? That is an issue that will probably concern researchers, when ML becomes mature and widely spread in software verification.

>>>>

Generally, state-of-the-art verification methodologies for embedded systems (including ECPSs) generate test vectors (with constraints) and use some assertion-based verification and high-level processor models, during simulation~\cite{Behrend15,Lettnin09}, as shown in Figure~\ref{verification-methodologies}. 
%
\begin{figure}[h]
	\centering
	\includegraphics[scale=0.5]{figure4.jpg}
	\caption{Verification methodologies for embedded systems.}
	\label{verification-methodologies}
\end{figure}

@@

Indeed, the first two aspects are of extreme relevance in micro-grids and cyber-physical systems, in order to ensure reliability, which is a key issue for (smart) cities, industries, and consumers, and the third one is essential in systems that implement device models, such as digital filters and controllers, which present a behavior that is highly dependent on signal inputs and outputs and whose deployment may be heavily affected by hardware restrictions. The fourth aspect deals with code that relies on existing infrastructures and must be compliant with those, such as Linux kernel modules. The fifth aspect, in turn, is inherent to a large number of embedded systems from  telecommunications, control systems, and medical devices, including ECPSs. In particular, software developed for those types of embedded system has been extensively tested and verified, and also optimized for efficiency over years of development. Therefore, when a new product is derived from a given platform, a lot of legacy code is usually reused for improving development time and code quality. The sixth aspect is related to evolving development processes and technologies, which may delay the application of suitable verification and synthesis approaches, if verifiers and synthesizers do not support different programming languages and interfaces. The seventh aspect highlights a subjective task in verification: where one must insert an evaluation point or assertion, in order to correct address a property. The eighth one is related to the widespread use of embedded systems in autonomous-vehicle navigation systems~\cite{Adouane16}, which demands optimization solving during their execution for a wide range of functions, including non-linear and non-convex problems using fixed- and floating-point arithmetic. The ninth aspect is a consequence of changes in environment or different applications and scenarios, which may present new problems to embedded systems that did not exist or were not tackled during their development. Such a challenge is also closely related to ML techniques, given that they may be integrated into commercial systems and have the potential to devise new and refined control strategies, which must then be identified, checked, and validated. For instance, a diagnostic system may employ techniques that make it able to learn new tumor patterns and them warn their presence on patients' bodies, but a wrong updated model may compromise earlier traditional assessments and erroneously perform new ones, which should be verified and validated. Finally, the latter also raises another question: an embedded system must be checked only when it is developed/created or also during its life cycle, in order to ensure that improved models and actions are sound and reliable? That is an issue that will probably concern researchers, when ML becomes mature and widely spread in software verification.
